## Experiment 1b
This study was conducted to further confirm that the moral character information influence the perceptual decision making instead of other factors such as the familiarity of words. To do so, we selected different words whose dominant meaning is related to moral character but with similar level of familiarity between different words.

### Method

#### Participants
`r df1b.T.basic$N` college students (`r df1b.T.basic$Nf` female, age = `r df1b.T.basic$Age_mean` $\pm$ `r df1b.T.basic$Age_sd` years) participated. `r df1b.T.basic$N_thu` of them were recruited from Tsinghua University community in 2014; `r df1b.T.basic$N_wzu` were recruited from Wenzhou University in 2017. All participants were right-handed except one, and all had normal or corrected-to-normal vision. Informed consent was obtained from all participants prior to the experiment according to procedures approved by the local ethics committees. `r nrow(df1b.excld.sub)` participant’s data were excluded from analysis because nearly random level of accuracy, leaving `r df1b.v.basic$N` participants (`r df1b.v.basic$Nf` female, age = `r df1b.v.basic$Age_mean` $\pm$ `r df1b.v.basic$Age_sd` years).

### Stimuli and Tasks
Three geometric shapes (triangle, square, and circle, with 3.7º × 3.7º of visual angle) were presented above a white fixation cross subtending 0.8º × 0.8º of visual angle at the center of the screen. The three shapes were randomly assigned to three labels with different moral valence: a morally bad person (“恶人”, ERen), a morally good person (“善人”, ShanRen) or a morally neutral person (“常人”, ChangRen). The order of the associations between shapes and labels was counterbalanced across participants.

Three labels used in this experiment was selected based on the rating results from an independent survey, in which participants rated the familiarity, frequency, and concreteness of eight different words online. Of the eight words, three of them are morally positive (HaoRen, ShanRen, Junzi), two of them are morally neutral (ChangRen, FanRen), and three of them are morally negative (HuaiRen, ERen, LiuMang). An independent sample consist of 35 participants (22 females, age 20.6 ± 3.11) were recruited to rate these words. Based on the ratings (see supplementary materials Figure S1), we selected ShanRen, ChangRen, and ERen to represent morally positive, neutral, and negative person. 

![Ratings of words in exp 1b](exp1b/Familiarity_ratings/df1b_fami_rating.pdf){width=500px}

#### Procedure
For participants from both Tsinghua community and Wenzhou community, the procedure in the current study was exactly same as in experiment 1a.

### Data Analysis
Data was analyzed as in experiment 1a. 

### Results
#### NHST

```{r 'ex1b-dprime-rt', fig.cap="RT and *d* prime of Experiment 1b.", fig.height=4.5, fig.width=9, warning=FALSE}
# rtdata <- df1b.v.rt_m %>% dplyr::filter(Matchness == "Match") %>% dplyr::rename(RT = RT_m)

# Mplots(expName = 'exp1b', df1b.v.dprime_l,rtdata)

p_1b_d_rt <- Val_plot_NHST(df.rt = df1b.v.rt_m, df.d = df1b.v.dprime_l)
```

Figure \@ref(fig:ex1b-dprime-rt) shows *d* prime and reaction times of experiment 1b. 

##### d prime

```{r 1b_dprime, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# anova for d prime
df1b_dprime_anova <- afex::aov_ez('Subject','dprime',df1b.v.dprime_l, within = c('Valence'))
df1b_dprime_anova_apa <- df1b_dprime_anova %>% papaja::apa_print.afex_aov()

posthoc_1b_d <- emmeans::emmeans(df1b_dprime_anova, "Valence") # compare each valence for both self and other condition
#pairs(posthoc_1b_d)
```
Repeated measures ANOVA revealed main effect of valence, `r df1b_dprime_anova_apa$full$Valence`. Paired t test showed that the Good-Person condition (1.87 $\pm$ 0.102) was with greater *d* prime than Neutral condition (1.44 $\pm$ 0.101, *t*(51) = 5.945, *p* < 0.001). We also found that the Bad-Person condition (1.67 $\pm$ 0.11) has also greater *d* prime than neutral condition , *t*(51) = 3.132, *p* = 0.008). There Good-person condition was also slightly greater than the bad condition, *t*(51) = 2.265, *p* = 0.0701.

##### Reaction times

```{r 1b_RT, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
df1b_RT_anova <- afex::aov_ez('Subject','RT_m',df1b.v.rt_m, within = c('Matchness','Valence'))
df1b_RT_anova_apa <- df1b_RT_anova %>% papaja::apa_print.afex_aov()

df1b.v.rt_m1 <- df1b.v %>%
  dplyr::filter(ACC == 1 & Matchness == "Match") %>%
  dplyr::group_by(Site,Subject,Matchness, Valence) %>%
  dplyr::summarise(RT_m = mean(RT),
                   Ntrial = length(RT)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Valence = factor(Valence, levels = c("Good","Neutral","Bad")))

df1b.v.rt_m %>%
  dplyr::group_by(Matchness, Valence) %>%
  dplyr::summarise(mean = mean(RT_m),
                   sd = sd(RT_m))

df1b_RT_anova_m <- afex::aov_ez('Subject','RT_m', df1b.v.rt_m1,     # using afex's function 
                                  within = c('Valence'))
df1b_RT_anova_m_apa <- df1b_RT_anova_m %>% papaja::apa_print.afex_aov()

df1b.v.rt_m2 <- df1b.v %>%
  dplyr::filter(ACC == 1 & Matchness == "Mismatch") %>%
  dplyr::group_by(Site,Subject,Matchness, Valence) %>%
  dplyr::summarise(RT_m = mean(RT),
                   Ntrial = length(RT)) %>%
  dplyr::ungroup()

df1b_RT_anova_nm <- afex::aov_ez('Subject','RT_m',df1b.v.rt_m2,     # using afex's function 
                                  within = c('Valence'))
df1b_RT_anova_nm_apa <- df1b_RT_anova_nm %>% papaja::apa_print.afex_aov()
posthoc_1b_rt <- emmeans::emmeans(df1b_RT_anova_m, "Valence") # compare each valence for both self and other condition
# pairs(posthoc_1b_rt)
```
We found interaction between Matchness and Valence (`r df1b_RT_anova_apa$full$Matchness_Valence`) and then analyzed the matched trials and mismatched trials separately, as in experiment 1a. For matched trials, we found the effect of valence `r df1b_RT_anova_m_apa$full$Valence`. Post-hoc *t*-tests revealed that shapes associated with Good Person (684 $\pm$ 8.77) were responded faster than Neutral-Person (740 $\pm$ 9.84), (*t*(51) = -8.167, *p* < 0.001) and Bad Person (728 $\pm$ 9.15), *t*(51) = -5.724, *p* < 0.0001). While there was no significant differences between Neutral and Bad-Person condition (*t*(51) = 1.686, *p* = 0.221). For non-matched trials, there was no significant effect of Valence (`r df1b_RT_anova_nm_apa$full$Valence`).

#### BGLM
##### Signal detection theory analysis of accuracy
We fitted a Bayesian hierarchical GLM for SDT. The results showed that when the shapes were tagged with labels with different moral valence, the sensitivity ($d'$) and criteria ($c$) were both influence. For the $d'$, we found that the shapes tagged with morally good person (2.46, 95% CI[2.21 2.72]) is greater than shapes tagged with moral bad (2.07, 95% CI[1.83 2.32]), $P_{PosteriorComparison} = 1$. Shape tagged with morally good person is also greater than shapes tagged with neutral person (2.23, 95% CI[1.95 2.49]), $P_{PosteriorComparison} = 0.97$. Also, the shapes tagged with neutral person is greater than shapes tagged with morally bad person, $P_{PosteriorComparison} = 0.92$. 

Interesting, we also found the criteria for three conditions also differ, the shapes tagged with good person has the highest criteria (-1.01, [-1.14 -0.88]), followed by shapes tagged with neutral person(1.06, [-1.21 -0.92]), and then the shapes tagged with bad person(-1.11, [-1.25 -0.97]). However, pair-wise comparison showed that only showed strong evidence for the difference between good and bad conditions.

```{r 1b_BGLMM_sdt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
exp1b_sdt_m1 <- fun_sdt_val('1b')

summary(exp1b_sdt_m1)    # check summary
#pp_check(exp1b_sdt_m1)   # posterior predictive check

hypothesis(exp1b_sdt_m1, "ValenceGood:ismatch > ValenceNeutral:ismatch")  # 1
hypothesis(exp1b_sdt_m1, "ValenceGood:ismatch > ValenceBad:ismatch")      # .97
hypothesis(exp1b_sdt_m1, "ValenceNeutral:ismatch < ValenceBad:ismatch")   # 0.99
hypothesis(exp1b_sdt_m1, "ValenceGood > ValenceNeutral")  # 0.97
hypothesis(exp1b_sdt_m1, "ValenceGood > ValenceBad")      # 1
hypothesis(exp1b_sdt_m1, "ValenceNeutral > ValenceBad")   # 0.99

# extract the population level parameters
# criteria
# exp1b_sdt_p <- fun_plot_sdt_val(exp1b_sdt_m1)
exp1b_sdt_p <- exp1b_sdt_m1 %>%
  emmeans::emmeans( ~ ismatch | Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'criterion', 'd prime'),
                ismatch = factor(ismatch, levels = c('d prime', 'criterion')),
                Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad'))) %>%
  dplyr::filter(ismatch == 'd prime') %>%
  ggplot2::ggplot(aes(x = Valence, y = .value)) +
  tidybayes::stat_halfeye() + # position=position_dodge(width = 0.1)
  stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  ylab(expression(paste("Sensitivity ",italic("d'"), sep = ' '))) +
  # facet_grid(cols = vars(ismatch), scales = "free_y") +
  theme_classic() + 
  theme(axis.title.x = element_blank())
```
##### Reaction time

```{r 1b_BGLMM_rt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# fit a three-level hierarchical model for RT, didn't specify the prior
exp1b_rt_m1 <- fun_rt_val('1b')
#plot(exp1b_rt_m1, "b_")
summary(exp1b_rt_m1)  # n
#pp_check(exp1b_rt_m1)

# Population-Level Effects: 
#                    Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
# Intercept              -0.30      0.02    -0.33    -0.26 1.02      288      642  # baseline: mismatch:neutral = -.3
# ValenceBad              0.00      0.01    -0.01     0.01 1.00     3611     3116  # mismatch:neutral + mismatch:bad  = -.3
# ValenceGood             0.00      0.01    -0.01     0.01 1.00     2749     2691  # mismatch:neutral + mismatch:Good = -.3
# ismatch                -0.07      0.01    -0.09    -0.06 1.00     2203     2371  # mismatch:neutral + ismatch = (-0.30) + (-0.07) = -0.37
# ValenceBad:ismatch      0.02      0.01     0.00     0.05 1.00     2451     2495  # mismatch:neutral + ismatch + match:bad  = (-0.30) + (-0.07) + 0.02 = -0.35
# ValenceGood:ismatch    -0.04      0.02    -0.07    -0.01 1.00     1911     2326  # mismatch:neutral + ismatch + match:good = (-0.30) + (-0.07) +-0.04 = -0.41

hypothesis(exp1b_rt_m1, "ismatch < 0")  # Effect of matchness: Match < mis-match, p = 1
hypothesis(exp1b_rt_m1, "ValenceGood:ismatch < 0")  # Match good < Match Neutral, p = 0.99
hypothesis(exp1b_rt_m1, "ValenceBad:ismatch > 0")   # Match Bad > Match Neutral, p = 0.99
hypothesis(exp1b_rt_m1, "(ValenceGood:ismatch - ValenceBad:ismatch) < 0")   # Match Good < Match Bad, p = 1

#exp1b_rt_p <- fun_plot_rt_val(exp1b_rt_m1)
exp1b_rt_p <- exp1b_rt_m1 %>%
  emmeans::emmeans( ~ ismatch | Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'nonmatch', 'match'),
              Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad'))) %>%
  dplyr::filter(ismatch == 'match') %>%
  dplyr::rename(log_RT = .value) %>%
  dplyr::mutate(`Reaction times (ms)` = exp(log_RT)*1000) %>%
  ggplot2::ggplot(aes(x = Valence, y = `Reaction times (ms)`)) +
  tidybayes::stat_halfeye() +
  ggplot2::stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  #facet_grid(~ ismatch) +
  theme_classic() + 
  theme(axis.title.x = element_blank())
```

```{r plot-exp1b-BGLM, fig.cap="Exp1b: Results of Bayesian GLM analysis.",  fig.height=4.5, fig.width=9, warning=FALSE}
# library(patchwork)
# exp1b_rt_p + exp1b_sdt_p + plot_annotation(tag_levels = 'A')  + plot_layout(nrow = 1, byrow = FALSE)
```

We fitted a Bayesian hierarchical GLM for RTs, with a log-normal distribution as the link function. We used the posterior distribution of the regression coefficient to make statistical inferences. As in previous studies, the matched conditions are much faster than the mismatched trials ($P_{PosteriorComparison} = 1$). We focused on matched trials only, and compared different conditions: Good is faster than the neutral, $P_{PosteriorComparison} = .99$, it was also faster than the Bad condition, $P_{PosteriorComparison} = 1$. And the neutral condition is faster than the bad condition, $P_{PosteriorComparison} = .99$. However, the mismatched trials are largely overlapped. See Figure \@ref(fig:plot-exp1b-BGLM).

#### HDDM
We found that the shapes tagged with good person has higher drift rate and higher boundary separation than shapes tagged with both neutral and bad person. Also, the shapes tagged with neutral person has a higher drift rate than shapes tagged with bad person, but not for the boundary separation. Finally, we found that shapes tagged with bad person had longer non-decision time (see figure \@ref(fig:plot-exp1b-HDDM)).

```{r plot-exp1b-HDDM, fig.cap="Exp1b: Results of HDDM.",  fig.height=4.5, fig.width=9, warning=FALSE}
df1b.hddm.group.trace <- readr::read_csv(here::here('HDDM','df1b_group_traces.csv')) # this will keep the '(' and ')' in the column name

params_p <- df1b.hddm.group.trace %>%
  dplyr::mutate(sample = 1:nrow(.)) %>%
  dplyr::select(chain, sample, contains('Match') | contains('Mismatch')) %>%
  tidyr::pivot_longer(.,`a(Match.Bad)`:`t(Mismatch.Neutral)`, names_to = 'conditions', values_to = 'value') %>%
  tidyr::separate(., conditions, into = c('v1', 'valence'), sep= '[.]') %>%       # split into two part
  tidyr::separate(., v1, into = c('param', 'matchness'), sep = '[(]') %>%         # further split the first half into two part
  dplyr::mutate(valence = stringr::str_sub(.$valence, start = 1, end = -2)) %>%   # remove the last two elements ') ' from the strings
  dplyr::arrange(., param) %>%
  tidyr::pivot_wider(., id_cols = c('chain', 'sample', 'matchness', 'valence'), names_from = 'param', values_from = 'value')

p_1b_hddm <- params_p %>% 
  dplyr::mutate(valence = factor(valence, levels = c("Good", "Neutral", "Bad")),
                matchness = ifelse(matchness == 'Mismatch', 'Nonmatch', matchness)) %>%
  dplyr::filter(matchness == 'Match') %>%
  ggplot2::ggplot(., aes(x = v, y = a, group = valence, color = valence)) +
  geom_point() + 
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  #facet_grid(~ matchness) +
  ylab(expression(paste("Boundary separation ",italic("a"), sep = ' '))) +
  xlab(expression(paste("Drift rate ",italic("v"), sep = ' '))) +
  theme_bw()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          text=element_text(family='Times'),
          legend.title=element_blank(),
          legend.text = element_text(size =8),
          legend.position="bottom",
          plot.title = element_text(lineheight=.8, face="bold", size = 9, margin=margin(0,0,10,0)),
          axis.text = element_text (size = 8, color = 'black'),
          axis.title = element_text (size = 8),
          #axis.title.x = element_blank(),
          #axis.title.y = element_blank(),
          axis.line.x = element_line(color='black', size = 1),    # increase the size of font
          axis.line.y = element_line(color='black', size = 1),    # increase the size of font
          strip.text = element_text (size = 8, color = 'black'), # size of text in strips, face = "bold"
          panel.spacing = unit(3, "lines")
    ) 
```


### Discussion
These results confirmed the facilitation effect of positive moral valence on the perceptual matching task. This pattern of results mimic prior results demonstrating self-bias effect on perceptual matching [@Sui_2012_JEPHPP] and in line with previous studies that indirect learning of other’s moral reputation do have influence on our subsequent behavior (Fouragnan et al., 2013). 

