## Experiment 3b
In study 3a, participants had to remember 6 pairs of association, which cause high cognitive load during the whole experiment. To eliminate the influence of cognitive load, we conducted study 3b, in which participant learn three aspect of self and stranger separately in to consecutive task. We hypothesize that we will replicate the pattern of study 3a, i.e., the effect of moral valence only occurs for self-relevant conditions.
### Method

#### Participants
Study 3b were finished in 2017, at that time we have calculated that the effect size (Cohen’s $d$) of good-person (or good-self) vs. bad-person (or bad-other) was between 0.47 ~ 0.53, based on the data from Tsinghua community in study 1a, 1b, 2, 3a, 4a, and 4b. Based on this effect size, we estimated that 54 participants would allow we to detect the effect size of Cohen’s = 0.5 with 95% power and alpha = 0.05, using G*power 3.192 [@faul_statistical_2009]. Therefore, we planned to stop after we arrived this number. During the data collected at Wenzhou University, `r df3b.T.basic$N` participants (`r df3b.T.basic$Nf` females; 19 to 25 years of age, age = `r df3b.T.basic$Age_mean` $\pm$ `r df3b.T.basic$Age_sd`) came to the testing room and we tested all of them during a single day. All participants were right-handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all participants prior to the experiment according to procedures approved by a local ethics committee. `r nrow(df3b.excld.sub)` participants’ data were excluded from analysis because their over all accuracy was lower than 60%, 1 more participant was excluded because of zero hit rate for one condition, leaving `r df3b.v.basic$N` participants (`r df3b.v.basic$Nf`  females; 19 to 25 years old, age = `r df3b.v.basic$Age_mean` $\pm$ `r df3b.v.basic$Age_sd`). 

#### Design
Study 3b has the same experimental design as 3a, with a 2× 3× 2 within-subject design. The first variable was self-relevance, include two levels: self-relevant vs. stranger-relevant; the second variable was moral valence, include good, neutral and bad; the third variable was the matching between shape and label: match vs. mismatch.
 Stimuli.	The stimuli used in study 3b share the same parameters with experiment 3a. 6 shapes were included (triangle, square, circle, trapezoid, diamond, regular pentagon), as well as 6 labels, but the labels changed to “good self”, “neutral self”, “bad self”, “good him/her”, bad him/her”, “neutral him/her”, the stranger’s label is consistent with participants’ gender. Same as study 3a, we asked participant to chosen an unfamiliar name of their own gender to be the stranger before showing them the relationship. Note, because of implementing error, the personal distance data did not collect for this experiment.

#### Stimuli
The stimuli used in study 3b is the same as in experiment 3a.

#### Procedure
In this experiment, participants finished two matching tasks, i.e., self-matching task, and other-matching task. In the self-matching task, participants first associate the three aspects of self to three different shapes, and then perform the matching task. In the other-matching task, participants first associate the three aspects of the stranger to three different shapes, and then perform the matching task. The order of self-task and other-task are counter-balanced among participants.
Different from experiment 3a, after presenting the stimuli pair for 100ms, participant has 1900 ms to response, and they feedback with both accuracy and reaction time.
As in study 3a, before each task, the instruction showed the meaning of each label to participants. The self-matching task and other-matching task were randomized between participants. Each participant finished 6 blocks, each have 120 trials.

#### Data Analysis
Same as experiment 3a.

### Results

#### NHST
```{r 'ex3b-dprime-rt', fig.cap="RT and *d* prime of Experiment 3a.", fig.height=6, fig.width=10, warning=FALSE}
#rtdata <- df3b.v.rt_m %>% dplyr::filter(Matchness == "Match") %>% dplyr::rename(RT = RT_m)
#Mplots(expName = 'exp3b', df3b.v.dprime_l,rtdata)

Val_id_plot_NHST(df.rt = df3b.v.rt_m, df.d = df3b.v.dprime_l)

```

Figure \@ref(fig:ex3a-dprime-rt) shows *d* prime and reaction times of experiment 3a. Less than 5% correct trials with less than 200ms reaction times were excluded.

##### d prime

```{r 3b_dprime, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# anova for d prime
df3b_dprime_anova <- afex::aov_ez('Subject','dprime',df3b.v.dprime_l, within = c('Identity','Valence'))
df3b_dprime_anova_apa <- df3b_dprime_anova %>% papaja::apa_print.afex_aov()

posthoc_3b_d <- emmeans::emmeans(df3b_dprime_anova, ~ Valence| Identity) # compare each valence for both self and other condition
pairs(posthoc_3b_d)

df3b_dprime_s_anova <- df3b.v.dprime_l %>%
  dplyr::filter(Identity == 'Self') %>%
  afex::aov_ez('Subject','dprime', ., within = c('Valence'))
df3b_dprime_s_anova_apa <- df3b_dprime_s_anova %>% papaja::apa_print.afex_aov()
posthoc_3b_d_s <- emmeans::emmeans(df3b_dprime_s_anova, "Valence")
pairs(posthoc_3b_d_s)

df3b_dprime_o_anova <- df3b.v.dprime_l %>%
  dplyr::filter(Identity == 'Other') %>%
  afex::aov_ez('Subject','dprime', ., within = c('Valence'))
df3b_dprime_o_anova_apa <- df3b_dprime_o_anova %>% papaja::apa_print.afex_aov()
posthoc_3b_d_o <- emmeans::emmeans(df3b_dprime_o_anova, "Valence")
pairs(posthoc_3b_d_o)

```
There was no evidence for the main effect of valence, `r df3b_dprime_anova_apa$full$Valence`, but we found a main effect of self-relevance, `r df3b_dprime_anova_apa$full$Identity`, as well as the interaction, `r df3b_dprime_anova_apa$full$Identity_Valence`. 

We then conducted separated ANOVA for self-referential and other-referential trials. The valence effect was shown for the self-referential conditions, `r df3b_dprime_s_anova_apa$full$Valence`. Post-hoc test revealed that the Good-Self condition (2.15 $\pm$ 0.12) was with greater *d* prime than Neutral condition (1.83 $\pm$ 0.12, *t*(34) = 3.36, *p* = 0.0031), and Bad-self condition (1.87 $\pm$ 0.12),  *t*(34) = 2.955, *p* = 0.01. There was difference between neutral and bad condition, *t*(34) = -0.039, *p* = 0.914. However, no effect of valence was found for the other-referential condition `r df3b_dprime_o_anova_apa$full$Valence`.

##### Reaction time

```{r 3b_RT, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
df3b_RT_anova <- afex::aov_ez('Subject','RT_m',df3b.v.rt_m,     # using afex's function 
                                  within = c('Matchness','Identity','Valence'))
df3b_RT_anova_apa <- df3b_RT_anova %>% papaja::apa_print.afex_aov()
```

We found interaction between Matchness and Valence (`r df3b_RT_anova_apa$full$Matchness_Valence`) and then analyzed the matched trials and nonmatch trials separately, as in previous experiments.

```{r 3b_RT_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# match trials
df3b_RT_anova_m <- df3b.v.rt_m %>%
  dplyr::filter(Matchness == "Match") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Identity','Valence'))

df3b_RT_anova_m_apa <- df3b_RT_anova_m %>% papaja::apa_print.afex_aov()

#posthoc_3b_rt <- emmeans::emmeans(df3b_RT_anova_m, c('Identity',"Valence")) # compare each valence for both self and other condition
# pairs(posthoc_3b_rt)

df3b_RT_anova_m_s <- df3b.v.rt_m %>%
  dplyr::filter(Matchness == "Match" & Identity == "Self") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Valence'))

df3b_RT_anova_m_s_apa <- df3b_RT_anova_m_s %>% papaja::apa_print.afex_aov()

posthoc_3b_rt_m_s <- emmeans::emmeans(df3b_RT_anova_m_s, 'Valence')
pairs(posthoc_3b_rt_m_s)

df3b_RT_anova_m_o <- df3b.v.rt_m %>%
  dplyr::filter(Matchness == "Match" & Identity == "Other") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Valence'))

df3b_RT_anova_m_o_apa <- df3b_RT_anova_m_o %>% papaja::apa_print.afex_aov()

# nonmatch trials
df3b_RT_anova_nm <- df3b.v.rt_m %>%
  dplyr::filter(Matchness == "Mismatch") %>%
  afex::aov_ez('Subject','RT_m', ., within = c('Identity','Valence'))

df3b_RT_anova_nm_apa <- df3b_RT_anova_nm %>% papaja::apa_print.afex_aov()
```
For the match trials, we found that the interaction between identity and valence, `r df3b_RT_anova_m_apa$full$Identity_Valence`, as well as the main effect of valence `r df3b_RT_anova_m_apa$full$Valence`, but not the effect of identity `r df3b_RT_anova_m_apa$full$Identity`. As for the *d* prime, we separated analyzed the self-referential and other-referential trials. For the Self-referential trials, we found the main effect of valence, `r df3b_RT_anova_m_s_apa$full$Valence`; for the other-referential trials, the effect of valence is weaker, `r df3b_RT_anova_m_o_apa$full$Valence`. We then focused on the self conditions: the good-self condition (713 $\pm$ 12) is faster than neutral- (776 $\pm$ 11.8), *t*(34) = -7.396, *p* < .0001 , and bad-self (772 $\pm$ 10.1) conditions,  *t*(34) = -5.66, *p* < .0001. But there is not difference between neutral- and bad-self conditions, *t*(34) = 0.481, *p* = 0.881.

For the nonmatch trials, we didn't found any strong effect: identity, `r df3b_RT_anova_nm_apa$full$Identity`, valence `r df3b_RT_anova_nm_apa$full$Valence`, or interaction between the two `r df3b_RT_anova_nm_apa$full$Identity_Valence`.


#### BGLM
##### Signal detection theory analysis of accuracy

```{r 3b_BGLMM_sdt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

exp3b_sdt_m1 <- fun_sdt_val_id('3b')

summary(exp3b_sdt_m1)    # check summary

# check fixed and varying effect using bayestestR
bayestestR::describe_posterior(
  exp3b_sdt_m1,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all"
)
#pp_check(exp3b_sdt_m1)   # posterior predictive check

# d-prime
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood:ismatch> IdentitySelf:ValenceNeutral:ismatch")  # 1
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood:ismatch> IdentitySelf:ValenceBad:ismatch")  # 1
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceNeutral:ismatch> IdentitySelf:ValenceBad:ismatch")  # .55
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceGood:ismatch> IdentityOther:ValenceNeutral:ismatch")  # .85
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceGood:ismatch> IdentityOther:ValenceBad:ismatch ")  # .71
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceNeutral:ismatch> IdentityOther:ValenceBad:ismatch")  # .27

hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood:ismatch> IdentityOther:ValenceGood:ismatch")  # .73
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceNeutral:ismatch> IdentityOther:ValenceNeutral:ismatch")  # .05
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceBad:ismatch> IdentityOther:ValenceBad:ismatch")  # .0

hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood > IdentitySelf:ValenceNeutral")  # .73
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood > IdentitySelf:ValenceBad")  # .9
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceNeutral > IdentitySelf:ValenceBad")  # .49
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceGood > IdentityOther:ValenceNeutral")  # .68
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceGood > IdentityOther:ValenceBad")  # .92
hypothesis(exp3b_sdt_m1, "IdentityOther:ValenceNeutral> IdentityOther:ValenceBad")  # .8

hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceGood > IdentityOther:ValenceGood")  # .92
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceNeutral > IdentityOther:ValenceNeutral")  # .76
hypothesis(exp3b_sdt_m1, "IdentitySelf:ValenceBad > IdentityOther:ValenceBad")  # .96

# extract the population level parameters
# criteria
exp3b_sdt_p <- exp3b_sdt_m1 %>%
  emmeans::emmeans( ~ ismatch | Identity| Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'criterion', 'd prime'),
                ismatch = factor(ismatch, levels = c('d prime', 'criterion')),
                Valence = factor(Valence, levels = c('Bad', 'Neutral',  'Good')),
                Identity = factor(Identity, levels = c('Self', 'Other'))) %>%
  ggplot2::ggplot(aes(x = Valence, y = .value, group = Identity, color = Identity)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() + # position=position_dodge(width = 0.1)
  stat_summary(aes(group = Identity, color = Identity), fun.y = mean, geom = "line"
               #,position=position_dodge(width = 0.1)
               ) +
  #scale_fill_brewer() +
  facet_grid(~ ismatch) +
  theme_classic()
```
We found that the *d* prime is greater when shapes were associated with good self condition than with neutral self or bad self, but shapes associated with bad self and neutral self didn't show differences. comparing the self vs other under three condition revealed that shapes associated with good self is greater than with good other, but with a weak evidence. In contrast, for both neutral and bad valence condition, shapes associated with other had greater *d* prime than with self.

##### Reaction time

```{r 3b_BGLMM_rt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
exp_name <- '3a'
exp3b_rt_m1 <- fun_rt_val_id(exp_name)

summary(exp3b_rt_m1)  # n

bayestestR::describe_posterior(
  exp3b_rt_m1,
  effects = "all",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all"
)

#pp_check(exp3b_rt_m1)
rg <- emmeans::ref_grid(exp3b_rt_m1)
em <- emmeans::emmeans(rg, 'ismatch')
summary(em, point.est = median)
emmeans::joint_tests(exp3b_rt_m1)

exp3b_rt_p <- exp3b_rt_m1 %>%
  emmeans::emmeans( ~ ismatch | Identity| Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'nonmatch', 'match'),
              Valence = factor(Valence, levels = c('Bad', 'Neutral',  'Good')),
              Identity = factor(Identity, levels = c('Self', 'Other'))) %>%
  dplyr::rename(log_RT = .value) %>%
  ggplot2::ggplot(aes(x = Valence, y = log_RT, group = Identity, color = Identity)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() +
  ggplot2::stat_summary(aes(group = Identity, color = Identity), fun.y = mean, geom = "line") +
  #scale_fill_brewer() +
  facet_grid(~ ismatch) +
  theme_classic()

emm1 <- emmeans::emmeans(exp3b_rt_m1, specs = pairwise ~ Identity | Valence | ismatch)
emm1$contrasts %>% summary(infer = TRUE, point.est = mean)

emm2 <- emmeans::emmeans(exp3b_rt_m1, specs = pairwise ~ Valence | Identity | ismatch)
emm2$contrasts %>% summary(infer = TRUE, point.est = mean)

```

```{r plot-exp3b-BGLM, fig.cap="exp3b: Results of Bayesian GLM analysis.",  fig.height=4.5, fig.width=9, warning=FALSE}
library(patchwork)
exp3b_sdt_p + exp3b_rt_p + plot_annotation(tag_levels = 'A')  + plot_layout(nrow = 1, byrow = FALSE)
```

In reaction times, we found that same trends in the match trials as in the RT: while the shapes associated with good self was greater than with good other (log mean diff = -0.02858, 95%HPD[-0.070898, 0.0154]), the direction is reversed for neutral and negative condition. see Figure \@ref(fig:plot-exp3b-BGLM) 

### HDDM

```{r plot-exp3b-HDDM, fig.cap="exp3b: Results of HDDM.",  fig.height=8, fig.width=9, warning=FALSE}
df3b.hddm.group.trace <- readr::read_csv(here::here('HDDM','df3b_group_traces.csv')) # this will keep the '(' and ')' in the column name

params_p <- df3b.hddm.group.trace %>%
  dplyr::mutate(sample = 1:nrow(.)) %>%
  dplyr::select(chain, sample, contains('Match') | contains('Mismatch')) %>%
  tidyr::pivot_longer(.,`a(Other.Match.Bad)`:`t(Self.Mismatch.Neutral)`, names_to = 'conditions', values_to = 'value') %>%
  tidyr::separate(., conditions, into = c('v1', 'matchness','valence'), sep= '[.]') %>%       # split into two part
  tidyr::separate(., v1, into = c('param', 'identity'), sep = '[(]') %>%         # further split the first half into two part
  dplyr::mutate(valence = stringr::str_sub(.$valence, start = 1, end = -2)) %>%   # remove the last two elements ') ' from the strings
  dplyr::arrange(., param) %>%
  tidyr::pivot_wider(., id_cols = c('chain', 'sample', 'matchness', 'identity', 'valence'), names_from = 'param', values_from = 'value')

params_p %>% 
  dplyr::mutate(valence = factor(valence, levels = c("Good", "Neutral", "Bad")),
                matchness = ifelse(matchness == 'Mismatch', 'Nonmatch', matchness)) %>%
  ggplot2::ggplot(., aes(x = v, y = a, group = valence, color = valence)) +
  geom_point() + 
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(identity ~ matchness) +
  #facet_grid(~ matchness) +
  ylab(expression(paste("Boundary separation ",italic("a"), sep = ' '))) +
  xlab(expression(paste("Drift rate ",italic("v"), sep = ' '))) +
  theme_bw()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          text=element_text(family='Times'),
          legend.title=element_blank(),
          legend.text = element_text(size =16),
          plot.title = element_text(lineheight=.8, face="bold", size = 18, margin=margin(0,0,20,0)),
          axis.text = element_text (size = 16, color = 'black'),
          axis.title = element_text (size = 16),
          #axis.title.x = element_blank(),
          #axis.title.y = element_blank(),
          axis.line.x = element_line(color='black', size = 1),    # increase the size of font
          axis.line.y = element_line(color='black', size = 1),    # increase the size of font
          strip.text = element_text (size = 16, color = 'black'), # size of text in strips, face = "bold"
          panel.spacing = unit(3, "lines")
    ) 
```

We fitted our data with HDDM, using the response-coding [also see @Hu_2020_GoodSelf]. We estimated separate drift rate ($v$), non-decision time ($T_{0}$), and boundary separation ($a$) for each condition. We found that the shapes tagged with good person has higher drift rate and higher boundary separation than shapes tagged with both neutral and bad person. Also, the shapes tagged with neutral person has a higher drift rate than shapes tagged with bad person, but not for the boundary separation. Finally, we found that shapes tagged with bad person had longer non-decision time (see figure \@ref(fig:plot-exp3b-HDDM))).