## Experiment 6a: EEG study 1
Experiment 6a was conducted to study the neural correlates of the positive prioritization effect. The behavioral paradigm is same as experiment 2. 

### Method

#### Participants
`r df6a.T.basic$N` college students (`r df6a.T.basic$Nf` female, age = `r df6a.T.basic$Age_mean` $\pm$ `r df6a.T.basic$Age_sd`) participated the current study, all of them were from Tsinghua University in 2014. Informed consent was obtained from all participants prior to the experiment according to procedures approved by a local ethics committee. No participant was excluded from behavioral analysis.

### Experimental design
The experimental design of this experiment is same as experiment 2:  a 3 × 2 within-subject design with moral valence (good, neutral and bad associations) and matchness between shape and label (match vs. mismatch for the personal association) as within-subject variables. 

#### Stimuli
Three geometric shapes (triangle, square and circle, each 4.6º × 4.6º of visual angle) were presented at the center of screen for 50 ms after 500ms of fixation (0.8º × 0.8º of visual angle). The association of the three shapes to bad person (“坏人, HuaiRen”), good person (“好人, HaoRen”) or ordinary  person (“常人, ChangRen”) was counterbalanced across participants. The words bad person, good person or ordinary  person (3.6º × 1.6º) was also displayed at the center fo the screen. Participants had to judge whether the pairings of label and shape matched (e.g., Does the circle represent a bad person?). The experiment was run on a PC using E-prime software (version 2.0). These stimuli were displayed on a 22-in CRT monitor (1024×768 at 100Hz).
We used backward masking to avoid over-processing of the moral words, in which a scrambled picture were presented for 900 ms after the label. Also, to avoid the ceiling effect on accuracy, shapes were presented on a noisy background based on our pilot studies. The noisy images were made by scrambling a picture of 3/4gray and ¼ white at resolution of 2 × 2 pixel. 

#### Procedure
The procedure was similar to Experiment 2. Participants finished 9 blocks of trial, each with 120 trials. In total, participants finished 180 trials for each combination of condition.

As in experiment 2 (Sui, He, & Humphreys, 2012), subjects first learned the associations between labels and shapes and then completed a shape-label matching task (e.g., good person-triangle). In each trial of the matching task, a fixation were first presented for 500 ms, followed by a 50 ms label; then, a scrambled picture presented 900 ms. After the backward mask, the shape were presented on a noisy background for 50ms. Participant have to response in 1000ms after the presentation of the shape, and finally, a feedback screen was presented for 500 ms (see figure 1). The inter-trial interval (ITI) were randomly varied at the range of 1000 ~ 1400 ms. 

All the stimuli were presented on a gray background (RGB: 127, 127, 127). E-primed 2.0 was used to present stimuli and collect behavioral results. Data were collected and analyzed when accuracy performance in total reached 60%. 

### Data Analysis
Data was analyzed as in experiment 1a. 

### Results
#### NHST

```{r 'ex6a-dprime-rt', fig.cap="RT and *d* prime of Experiment 6a.", fig.height=6, fig.width=15, warning=FALSE}
p_6a_d_rt <- Val_plot_NHST(df.rt = df6a.v.rt_m, df.d = df6a.v.dprime_l)

```

Only the behavioral results were reported here. Figure \@ref(fig:ex6a-dprime-rt) shows *d* prime and reaction times of experiment 6a.

##### d prime
```{r analyzing for d prime_e6a, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# anova for d prime with 2*2 design
df6a_dprime_anova <- afex::aov_ez('Subject','dprime',df6a.v.dprime_l,  # using afex's function 
                                  within = c('Valence'))
df6a_dprime_anova_apa <- df6a_dprime_anova %>% papaja::apa_print.afex_aov()

posthoc_6a_d <- lsmeans::lsmeans(df6a_dprime_anova, specs = 'Valence')
graphics::pairs(posthoc_6a_d)
# plot(posthoc_5a_d, comparisons = TRUE)
```
We conducted repeated measures ANOVA, with moral valence as independent variable. The results revealed the main effect of valence (`r df6a_dprime_anova_apa$full$Valence`). Post-hoc analysis revealed that shapes link with Good person (mean = 3.13, SE = 0.109) is greater than Neutral condition (mean = 2.88, SE = 0.14),*t* = 2.916, *df* = 24, *p* = 0.02, p-value adjusted by Tukey method, but the *d* prime between Good and bad (mean = 3.03, SE = 0.142) (*t* = 1.512, *df* = 24, *p* = 0.3034, p-value adjusted by Tukey method), bad and neutral (*t* = 1.599, *df* = 24, *p* = 0.2655, p-value adjusted by Tukey method) were not significant.

##### Reaction times.
The results of reaction times of matchness trials showed similar pattern as the *d* prime data.
```{r 6a_RT, echo=FALSE, results='hide', warning=FALSE, message=FALSE}

df6a_RT_anova <- afex::aov_ez('Subject','RT_m',df6a.v.rt_m,     # using afex's function 
                                  within = c('Matchness','Valence'))
df6a_RT_anova_apa <- df6a_RT_anova %>% papaja::apa_print.afex_aov()

# match trials
df6a.v.rt_m1 <- df6a.v %>%
  dplyr::filter(ACC == 1 & Matchness == "Match") %>%
  dplyr::group_by(Site,Subject,Matchness, Valence) %>%
  dplyr::summarise(RT_m = mean(RT),
                   Ntrial = length(RT)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Valence = factor(Valence, levels = c("Good","Neutral","Bad")))

df6a_RT_anova_m <- afex::aov_ez('Subject','RT_m',df6a.v.rt_m1,     # using afex's function 
                                  within = c('Valence'))
df6a_RT_anova_m_apa <- df6a_RT_anova_m %>% papaja::apa_print.afex_aov()

posthoc_6a_rt <- emmeans::emmeans(df6a_RT_anova_m, "Valence") # compare each valence for both self and other condition
# pairs(posthoc_6a_rt)

# Mismatch trials
df6a.v.rt_m2 <- df6a.v %>%
  dplyr::filter(ACC == 1 & Matchness == "Mismatch") %>%
  dplyr::group_by(Site,Subject,Matchness, Valence) %>%
  dplyr::summarise(RT_m = mean(RT),
                   Ntrial = length(RT)) %>%
  dplyr::ungroup()

df6a_RT_anova_nm <- afex::aov_ez('Subject','RT_m', df6a.v.rt_m2,     # using afex's function 
                                  within = c('Valence'))
df6a_RT_anova_nm_apa <- df6a_RT_anova_nm %>% papaja::apa_print.afex_aov()

```

We found intercation between Matchness and Valence (`r df6a_RT_anova_apa$full$Matchness_Valence`) and then analyzed the matched trials and mismatched trials separately, as in experiment 2. For matched trials, we found the effect of valence `r df6a_RT_anova_m_apa$full$Valence`. For non-matched trials, there was no significant effect of Valence (`r df6a_RT_anova_nm_apa$full$Valence`). Post-hoc *t*-tests revealed that shapes associated with Good Person (mean = 550, SE = 13.8) were responded faster than Neutral-Person (501, SE = 14.7), (*t*(24) = -5.171, *p* = 0.0001) and Bad Person (523, SE = 16.3), *t*(24) = -8.137, *p* < 0.0001)., and Neutral is faster than Bad-Person condition (*t*(32) = -3.282, *p* = 0.0085).

#### BGLM
##### Signal detection theory analysis of accuracy

```{r 6a_BGLMM_sdt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
exp6a_sdt_m1 <- fun_sdt_val('6a')

summary(exp6a_sdt_m1)    # check summary
#pp_check(exp1b_sdt_m1)   # posterior predictive check

hypothesis(exp6a_sdt_m1, "ValenceGood:ismatch > ValenceNeutral:ismatch")  # .97
hypothesis(exp6a_sdt_m1, "ValenceGood:ismatch > ValenceBad:ismatch")      # .77
hypothesis(exp6a_sdt_m1, "ValenceNeutral:ismatch < ValenceBad:ismatch")   # 0.9
hypothesis(exp6a_sdt_m1, "ValenceGood > ValenceNeutral")  # 0.83
hypothesis(exp6a_sdt_m1, "ValenceGood > ValenceBad")      # .99
hypothesis(exp6a_sdt_m1, "ValenceNeutral > ValenceBad")   # 0.87

# extract the population level parameters
# criteria
# exp6a_sdt_p <- fun_plot_sdt_val(exp6a_sdt_m1)

exp6a_sdt_p <- exp6a_sdt_m1 %>%
  emmeans::emmeans( ~ ismatch | Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'criterion', 'd prime'),
                ismatch = factor(ismatch, levels = c('d prime', 'criterion')),
                Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad'))
                #,Identity = factor(Identity, levels = c('Self', 'Other'))
                ) %>%
  ggplot2::ggplot(aes(x = Valence, y = .value)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() + # position=position_dodge(width = 0.1)
  stat_summary(aes(group = NA), fun.y = mean, geom = "line"
               #,position=position_dodge(width = 0.1)
               ) +
  #scale_fill_brewer() +
  facet_grid(cols = vars(ismatch), scales = "free_y") +
  theme_classic()
```
##### Reaction time

```{r 6a_BGLMM_rt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# fit a three-level hierarchical model for RT, didn't specify the prior
exp6a_rt_m1 <- fun_rt_val('6a')
#plot(exp6a_rt_m1, "b_")
summary(exp6a_rt_m1)  # n
#pp_check(exp1b_rt_m1)

hypothesis(exp6a_rt_m1, "ismatch < 0")  # Effect of matchness: Match < mis-match, p = 1
hypothesis(exp6a_rt_m1, "ValenceGood:ismatch < 0")  # Match good < Match Neutral, p = 0.99
hypothesis(exp6a_rt_m1, "ValenceBad:ismatch > 0")   # Match Bad > Match Neutral, p = 0.99
hypothesis(exp6a_rt_m1, "(ValenceGood:ismatch - ValenceBad:ismatch) < 0")   # Match Good < Match Bad, p = 1

# exp6a_rt_p <- fun_plot_rt_val(exp6a_rt_m1)

exp6a_rt_p <- exp6a_rt_m1 %>%
  emmeans::emmeans( ~ ismatch | Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'nonmatch', 'match'),
              Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad'))) %>%
              #Identity = factor(Identity, levels = c('Self', 'Other'))
  dplyr::rename(log_RT = .value) %>%
  dplyr::mutate(`Reaction times (ms)` = exp(log_RT)*1000) %>%
  ggplot2::ggplot(aes(x = Valence, y = `Reaction times (ms)`)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() +
  ggplot2::stat_summary(aes(group = NA), fun.y = mean, geom = "line") +
  #scale_fill_brewer() +
  facet_grid(~ ismatch) +
  theme_classic()
```

```{r plot-exp6a-BGLM, fig.cap="Exp6a: Results of Bayesian GLM analysis.",  fig.height=4.5, fig.width=9, warning=FALSE}
# library(patchwork)
# exp6a_sdt_p[[1]] + exp6a_sdt_p[[2]] + exp6a_sdt_p[[3]] + exp6a_sdt_p[[4]] + exp6a_rt_p[[1]] + exp6a_rt_p[[2]] + exp6a_rt_p[[3]] + exp6a_rt_p[[4]] + plot_annotation(tag_levels = 'A')  + plot_layout(nrow = 4, byrow = FALSE)
# exp6a_sdt_p + exp6a_rt_p + plot_annotation(tag_levels = 'A')  + plot_layout(nrow = 1, byrow = FALSE)
```

### HDDM

```{r plot-exp6a-HDDM, fig.cap="exp6a: Results of HDDM.",  fig.height=4.5, fig.width=9, warning=FALSE}
df6a.hddm.group.trace <- readr::read_csv(here::here('HDDM','df6a_group_traces.csv')) # this will keep the '(' and ')' in the column name

params_p <- df6a.hddm.group.trace %>%
  dplyr::mutate(sample = 1:nrow(.)) %>%
  dplyr::select(chain, sample, contains('Match') | contains('Mismatch')) %>%
  tidyr::pivot_longer(.,`a(Match.Bad)`:`t(Mismatch.Neutral)`, names_to = 'conditions', values_to = 'value') %>%
  tidyr::separate(., conditions, into = c('v1', 'valence'), sep= '[.]') %>%       # split into two part
  tidyr::separate(., v1, into = c('param', 'matchness'), sep = '[(]') %>%         # further split the first half into two part
  dplyr::mutate(valence = stringr::str_sub(.$valence, start = 1, end = -2)) %>%   # remove the last two elements ') ' from the strings
  dplyr::arrange(., param) %>%
  tidyr::pivot_wider(., id_cols = c('chain', 'sample', 'matchness', 'valence'), names_from = 'param', values_from = 'value')

p_6a_hddm <- params_p %>% 
  dplyr::mutate(valence = factor(valence, levels = c("Good", "Neutral", "Bad")),
                matchness = ifelse(matchness == 'Mismatch', 'Nonmatch', matchness)) %>%
  ggplot2::ggplot(., aes(x = v, y = a, group = valence, color = valence)) +
  geom_point() + 
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(~ matchness) +
  ylab(expression(paste("Boundary separation ",italic("a"), sep = ' '))) +
  xlab(expression(paste("Drift rate ",italic("v"), sep = ' '))) +
  theme_bw()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          text=element_text(family='Times'),
          legend.title=element_blank(),
          legend.text = element_text(size = 8),
          plot.title = element_text(lineheight=.8, face="bold", size = 9, margin=margin(0,0,10,0)),
          axis.text = element_text (size = 8, color = 'black'),
          axis.title = element_text (size = 8),
          #axis.title.x = element_blank(),
          #axis.title.y = element_blank(),
          axis.line.x = element_line(color='black', size = 1),    # increase the size of font
          axis.line.y = element_line(color='black', size = 1),    # increase the size of font
          strip.text = element_text (size = 8, color = 'black'), # size of text in strips, face = "bold"
          panel.spacing = unit(3, "lines")
    ) 
```

We fitted our data with HDDM, using the response-coding [also see @Hu_2020_GoodSelf]. We estimated separate drift rate ($v$), non-decision time ($T_{0}$), and boundary separation ($a$) for each condition. We found that, similar to experiment 2, the shapes tagged with good person has higher drift rate and higher boundary separation than shapes tagged with both neutral and bad person, but only for the self-referential condition. Also, the shapes tagged with neutral person has a higher drift rate than shapes tagged with bad person, but not for the boundary separation, and this effect also exist only for the  self-referential condition. 

Interestingly, we found that  in both self-referential and other-referential conditions, the shapes associated bad valence have higher drift rate and higher boundary separation. which might suggest that the shape associated with bad stimuli might be prioritized in the non-match trials (see figure \@ref(fig:plot-exp6a-HDDM)).