## Experiment 6b
Experiment 6b was conducted to study the neural correlates of the prioritization effect of positive self, i.e., the neural underlying of the behavioral effect found int experiment 3a. However, as in experiment 6a, the procedure of this experiment was modified to adopted to ERP experiment. 

### Method

#### Participants
`r df6b_d1.T.basic$N` college students (`r df6b_d1.T.basic$Nf` female, age = `r df6b_d1.T.basic$Age_mean` $\pm$ `r df6b_d1.T.basic$Age_sd`) participated the current study, all of them were recruited from Tsinghua University in 2016. Informed consent was obtained from all participants prior to the experiment according to procedures approved by a local ethics committee. For day 1's data, `r nrow(df6b_d1.excld.sub)` participant was excluded from the current analysis because of lower than 60% overall accuracy, remaining `r df6b_d1.v.basic$N` participants (`r df6b_d1.v.basic$Nf` female, age = `r df6b_d1.v.basic$Age_mean` $\pm$ `r df6b_d1.v.basic$Age_sd`). For day 2's data, one participant dropped out, leaving 22 participants  (`r df6b_d2.v.basic$Nf` female, age = `r df6b_d2.v.basic$Age_mean` $\pm$ `r df6b_d2.v.basic$Age_sd`), all of them has overall accuracy higher than 60%.

#### Design
The experimental design of this experiment is same as experiment 3:  a 2 × 3 × 2 within-subject design with self-relevance (self-relevant vs. other-relevant), moral valence (good, neutral, and bad) and matchness between shape and label (match vs. mismatch) as within-subject variables. 

#### Stimuli
As in experiment 3a, 6 shapes were included (triangle, square, circle, trapezoid, diamond, regular pentagon), as well as 6 labels (good self, neutral self, bad self, good person, bad person, neutral person). To match the concreteness of the label, we asked participant to chosen an unfamiliar name of their own gender to be the stranger.

#### Procedure
The procedure was similar to Experiment 2 and 6a. Subjects first learned the associations between labels and shapes and then completed a shape-label matching task. In each trial of the matching task, a fixation were first presented for 500 ms, followed by a 50 ms label; then, a scrambled picture presented 900 ms. After the backward mask, the shape were presented on a noisy background for 50ms. Participant have to response in 1000ms after the presentation of the shape, and finally, a feedback screen was presented for 500 ms. The inter-trial interval (ITI) were randomly varied at the range of 1000 ~ 1400 ms. 

All the stimuli were presented on a gray background (RGB: 127, 127, 127). E-primed 2.0 was used to present stimuli and collect behavioral results. Data were collected and analyzed when accuracy performance in total reached 60%. 

Because learning 6 associations was more difficult than 3 associations and participant might have low accuracy (see experiment 3a), the current study had extended to a two-day paradigm to maximizing the accurate trials that can be used in EEG data. At the first day, participants learnt the associations and finished 9 blocks of the matching task, each had 120 trials, without EEG recording. That is, each condition has 90 trials.

Participants came back to lab at the second day and finish the same task again, with EEG recorded. Before the EEG experiment, each participant finished a practice session again, if their accuracy is equal or higher than 85%, they start the experiment (one participant used lower threshold 75%). Each participant finished 18 blocks, each has 90 trials. One participant finished additional 6 blocks because of high error rate at the beginning, another two participant finished addition 3 blocks because of the technique failure in recording the EEG data. To increase the number of trials that can be used for EEG data analysis, matched trials has twice number as mismatched trials, therefore, for matched trials each participants finished 180 trials for each condition, for mismatched trials, each conditions has 90 trials.

#### Data Analysis
Same as experiment 3a. 

### Results of Day 1

#### NHST
```{r 'ex6b-d1-dprime-rt', fig.cap="RT and *d* prime of Experiment 6b.", fig.height=6, fig.width=10, warning=FALSE}

Val_id_plot_NHST(df.rt = df6b_d1.v.rt_m, df.d = df6b_d1.v.dprime_l)

```

Figure \@ref(fig:ex6b-d1-dprime-rt) shows *d* prime and reaction times of experiment 3b. Less than 5% correct trials with less than 200ms reaction times were excluded.

##### d prime

```{r 6b_d1_dprime, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# anova for d prime
df6b_d1_dprime_anova <- afex::aov_ez('Subject','dprime',df6b_d1.v.dprime_l, within = c('Identity','Valence'))
df6b_d1_dprime_anova_apa <- df6b_d1_dprime_anova %>% papaja::apa_print.afex_aov()

posthoc_6b_d1_d <- emmeans::emmeans(df6b_d1_dprime_anova, ~ Valence| Identity) # compare each valence for both self and other condition
pairs(posthoc_6b_d1_d)

df6b_d1_dprime_s_anova <- df6b_d1.v.dprime_l %>%
  dplyr::filter(Identity == 'Self') %>%
  afex::aov_ez('Subject','dprime', ., within = c('Valence'))
df6b_d1_dprime_s_anova_apa <- df6b_d1_dprime_s_anova %>% papaja::apa_print.afex_aov()
posthoc_6b_d1_d_s <- emmeans::emmeans(df6b_d1_dprime_s_anova, "Valence")
pairs(posthoc_6b_d1_d_s)

df6b_d1_dprime_o_anova <- df6b_d1.v.dprime_l %>%
  dplyr::filter(Identity == 'Other') %>%
  afex::aov_ez('Subject','dprime', ., within = c('Valence'))
df6b_d1_dprime_o_anova_apa <- df6b_d1_dprime_o_anova %>% papaja::apa_print.afex_aov()
posthoc_6b_d1_d_o <- emmeans::emmeans(df6b_d1_dprime_o_anova, "Valence")
pairs(posthoc_6b_d1_d_o)

```
There was no evidence for the main effect of valence, `r df6b_d1_dprime_anova_apa$full$Valence`, but we found a main effect of self-relevance, `r df6b_d1_dprime_anova_apa$full$Identity`, as well as the interaction, `r df6b_d1_dprime_anova_apa$full$Identity_Valence`. 

We then conducted separated ANOVA for self-referential and other-referential trials. The valence effect was shown for the self-referential conditions, `r df6b_d1_dprime_s_anova_apa$full$Valence`. Post-hoc test revealed that the Good-Self condition (2.15 $\pm$ 0.12) was with greater *d* prime than Neutral condition (1.83 $\pm$ 0.12, *t*(34) = 3.36, *p* = 0.0031), and Bad-self condition (1.87 $\pm$ 0.12),  *t*(34) = 2.955, *p* = 0.01. There was difference between neutral and bad condition, *t*(34) = -0.039, *p* = 0.914. However, no effect of valence was found for the other-referential condition `r df6b_d1_dprime_o_anova_apa$full$Valence`.

##### Reaction time

```{r 6b_d1_RT, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
df6b_d1_RT_anova <- afex::aov_ez('Subject','RT_m',df6b_d1.v.rt_m,     # using afex's function 
                                  within = c('Matchness','Identity','Valence'))
df6b_d1_RT_anova_apa <- df6b_d1_RT_anova %>% papaja::apa_print.afex_aov()
```

We found interaction between Matchness and Valence (`r df6b_d1_RT_anova_apa$full$Matchness_Valence`) and then analyzed the matched trials and nonmatch trials separately, as in previous experiments.

```{r 6b_d1_RT_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
# match trials
df6b_d1_RT_anova_m <- df6b_d1.v.rt_m %>%
  dplyr::filter(Matchness == "Match") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Identity','Valence'))

df6b_d1_RT_anova_m_apa <- df6b_d1_RT_anova_m %>% papaja::apa_print.afex_aov()

#posthoc_6b_rt <- emmeans::emmeans(df6b_d1_RT_anova_m, c('Identity',"Valence")) # compare each valence for both self and other condition
# pairs(posthoc_6b_rt)

df6b_d1_RT_anova_m_s <- df6b_d1.v.rt_m %>%
  dplyr::filter(Matchness == "Match" & Identity == "Self") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Valence'))

df6b_d1_RT_anova_m_s_apa <- df6b_d1_RT_anova_m_s %>% papaja::apa_print.afex_aov()

posthoc_6b_d1_rt_m_s <- emmeans::emmeans(df6b_d1_RT_anova_m_s, 'Valence')
pairs(posthoc_6b_d1_rt_m_s)

df6b_d1_RT_anova_m_o <- df6b_d1.v.rt_m %>%
  dplyr::filter(Matchness == "Match" & Identity == "Other") %>%
  afex::aov_ez('Subject','RT_m',., within = c('Valence'))

df6b_d1_RT_anova_m_o_apa <- df6b_d1_RT_anova_m_o %>% papaja::apa_print.afex_aov()

# nonmatch trials
df6b_d1_RT_anova_nm <- df6b_d1.v.rt_m %>%
  dplyr::filter(Matchness == "Mismatch") %>%
  afex::aov_ez('Subject','RT_m', ., within = c('Identity','Valence'))

df6b_d1_RT_anova_nm_apa <- df6b_d1_RT_anova_nm %>% papaja::apa_print.afex_aov()
```
For the match trials, we found that the interaction between identity and valence, `r df6b_d1_RT_anova_m_apa$full$Identity_Valence`, as well as the main effect of valence `r df6b_d1_RT_anova_m_apa$full$Valence`, but not the effect of identity `r df6b_d1_RT_anova_m_apa$full$Identity`. As for the *d* prime, we separated analyzed the self-referential and other-referential trials. For the Self-referential trials, we found the main effect of valence, `r df6b_d1_RT_anova_m_s_apa$full$Valence`; for the other-referential trials, the effect of valence is weaker, `r df6b_d1_RT_anova_m_o_apa$full$Valence`. We then focused on the self conditions: the good-self condition (713 $\pm$ 12) is faster than neutral- (776 $\pm$ 11.8), *t*(34) = -7.396, *p* < .0001 , and bad-self (772 $\pm$ 10.1) conditions,  *t*(34) = -5.66, *p* < .0001. But there is not difference between neutral- and bad-self conditions, *t*(34) = 0.481, *p* = 0.881.

For the nonmatch trials, we didn't found any strong effect: identity, `r df6b_d1_RT_anova_nm_apa$full$Identity`, valence `r df6b_d1_RT_anova_nm_apa$full$Valence`, or interaction between the two `r df6b_d1_RT_anova_nm_apa$full$Identity_Valence`.

#### BGLM
##### Signal detection theory analysis of accuracy

```{r 6b_d1_BGLMM_sdt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
exp_name <- '6b_d1'
exp6b_d1_sdt_m1 <- fun_sdt_val_id(exp_name)

#summary(exp6b_d1_sdt_m1)    # check summary

# check fixed and varying effect using bayestestR
bayestestR::describe_posterior(
  exp6b_d1_sdt_m1,
  effects = "fixed",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all"
)
#pp_check(exp6b_sdt_m1)   # posterior predictive check

# d-prime
hypothesis(exp6b_d1_sdt_m1, "ValenceGood:IdentitySelf:ismatch> ValenceNeutral:IdentitySelf:ismatch")    # 1
hypothesis(exp6b_d1_sdt_m1, "ValenceGood:IdentitySelf:ismatch> ValenceBad:IdentitySelf:ismatch")        # 1
hypothesis(exp6b_d1_sdt_m1, "ValenceNeutral:IdentitySelf:ismatch> ValenceBad:IdentitySelf:ismatch")     # .16
hypothesis(exp6b_d1_sdt_m1, "ValenceGood:IdentityOther:ismatch> ValenceNeutral:IdentityOther:ismatch")  # .44
hypothesis(exp6b_d1_sdt_m1, "ValenceGood:IdentityOther:ismatch> ValenceBad:IdentityOther:ismatch ")     # .32
hypothesis(exp6b_d1_sdt_m1, "ValenceNeutral:IdentityOther:ismatch> ValenceBad:IdentityOther:ismatch")    # .34

hypothesis(exp6b_d1_sdt_m1, "ValenceGood:IdentitySelf:ismatch> ValenceGood:IdentityOther:ismatch")  # .47
hypothesis(exp6b_d1_sdt_m1, "ValenceNeutral:IdentitySelf:ismatch> ValenceNeutral:IdentityOther:ismatch")  # .05
hypothesis(exp6b_d1_sdt_m1, "ValenceBad:IdentitySelf:ismatch> ValenceBad:IdentityOther:ismatch")  # .24

#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceGood > IdentitySelf:ValenceNeutral")  # .73
#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceGood > IdentitySelf:ValenceBad")  # .9
#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceNeutral > IdentitySelf:ValenceBad")  # .49
#hypothesis(exp6b_sdt_m1, "IdentityOther:ValenceGood > IdentityOther:ValenceNeutral")  # .68
#hypothesis(exp6b_sdt_m1, "IdentityOther:ValenceGood > IdentityOther:ValenceBad")  # .92
#hypothesis(exp6b_sdt_m1, "IdentityOther:ValenceNeutral> IdentityOther:ValenceBad")  # .8

#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceGood > IdentityOther:ValenceGood")  # .1
#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceNeutral > IdentityOther:ValenceNeutral")  # .
#hypothesis(exp6b_sdt_m1, "IdentitySelf:ValenceBad > IdentityOther:ValenceBad")  # .96

# extract the population level parameters
# criteria
exp6b_d1_sdt_p <- exp6b_d1_sdt_m1 %>%
  emmeans::emmeans( ~ ismatch | Identity| Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'criterion', 'd prime'),
                ismatch = factor(ismatch, levels = c('d prime', 'criterion')),
                Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad')),
                Identity = factor(Identity, levels = c('Self', 'Other'))) %>%
  ggplot2::ggplot(aes(x = Valence, y = .value, group = Identity, color = Identity)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() + # position=position_dodge(width = 0.1)
  stat_summary(aes(group = Identity, color = Identity), fun.y = mean, geom = "line"
               #,position=position_dodge(width = 0.1)
               ) +
  #scale_fill_brewer() +
  facet_grid(~ ismatch) +
  theme_classic()
```
We found that the *d* prime is greater when shapes were associated with good self condition than with neutral self or bad self, but shapes associated with bad self and neutral self didn't show differences. comparing the self vs other under three condition revealed that shapes associated with good self is greater than with good other, but with a weak evidence. In contrast, for both neutral and bad valence condition, shapes associated with other had greater *d* prime than with self.

##### Reaction time

```{r 6b_d1_BGLMM_rt, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
exp_name <- '6b_d1'
exp6b_d1_rt_m1 <- fun_rt_val_id(exp_name)

#summary(exp6b_rt_m1)  # n

bayestestR::describe_posterior(
  exp6b_d1_rt_m1,
  effects = "fixed",
  component = "all",
  test = c("p_direction", "p_significance"),
  centrality = "all"
)

#pp_check(exp6b_rt_m1)
rg <- emmeans::ref_grid(exp6b_d1_rt_m1)
em <- emmeans::emmeans(rg, 'ismatch')
summary(em, point.est = median)
emmeans::joint_tests(exp6b_d1_rt_m1)

exp6b_d1_rt_p <- exp6b_d1_rt_m1 %>%
  emmeans::emmeans( ~ ismatch | Identity| Valence) %>%
  tidybayes::gather_emmeans_draws() %>%
  dplyr::mutate(ismatch = ifelse(ismatch == 0, 'nonmatch', 'match'),
              Valence = factor(Valence, levels = c('Good', 'Neutral',  'Bad')),
              Identity = factor(Identity, levels = c('Self', 'Other'))) %>%
  dplyr::rename(log_RT = .value) %>%
  ggplot2::ggplot(aes(x = Valence, y = log_RT, group = Identity, color = Identity)) +
  #ggplot2::ggplot(aes(x = Valence, y = .value, group = .draw)) +
  #geom_line(alpha = .01) +
  tidybayes::stat_halfeye() +
  ggplot2::stat_summary(aes(group = Identity, color = Identity), fun.y = mean, geom = "line") +
  #scale_fill_brewer() +
  facet_grid(~ ismatch) +
  theme_classic()

emm1 <- emmeans::emmeans(exp6b_d1_rt_m1, specs = pairwise ~ Identity | Valence | ismatch)
emm1$contrasts %>% summary(infer = TRUE, point.est = mean)

emm2 <- emmeans::emmeans(exp6b_d1_rt_m1, specs = pairwise ~ Valence | Identity | ismatch)
emm2$contrasts %>% summary(infer = TRUE, point.est = mean)

```

```{r plot-exp6b-d1-BGLM, fig.cap="exp6b_d1: Results of Bayesian GLM analysis.",  fig.height=4.5, fig.width=9, warning=FALSE}
library(patchwork)
exp6b_d1_sdt_p + exp6b_d1_rt_p + plot_annotation(tag_levels = 'A')  + plot_layout(nrow = 1, byrow = FALSE)
```

In reaction times, we found that same trends in the match trials as in the RT: while the shapes associated with good self was greater than with good other (log mean diff = -0.02858, 95%HPD[-0.070898, 0.0154]), the direction is reversed for neutral and negative condition. see Figure \@ref(fig:plot-exp6b-d1-BGLM) 

### HDDM

```{r plot-exp6b-HDDM, fig.cap="exp6b: Results of HDDM (Day 1).",  fig.height=8, fig.width=9, warning=FALSE}
df6b.hddm.group.trace <- readr::read_csv(here::here('HDDM','df6b_group_traces.csv')) # this will keep the '(' and ')' in the column name

params_p <- df6b.hddm.group.trace %>%
  dplyr::mutate(sample = 1:nrow(.)) %>%
  dplyr::select(chain, sample, contains('Match') | contains('Mismatch')) %>%
  tidyr::pivot_longer(.,`a(Other.Match.Bad)`:`t(Self.Mismatch.Neutral)`, names_to = 'conditions', values_to = 'value') %>%
  tidyr::separate(., conditions, into = c('v1', 'matchness','valence'), sep= '[.]') %>%       # split into two part
  tidyr::separate(., v1, into = c('param', 'identity'), sep = '[(]') %>%         # further split the first half into two part
  dplyr::mutate(valence = stringr::str_sub(.$valence, start = 1, end = -2)) %>%   # remove the last two elements ') ' from the strings
  dplyr::arrange(., param) %>%
  tidyr::pivot_wider(., id_cols = c('chain', 'sample', 'matchness', 'identity', 'valence'), names_from = 'param', values_from = 'value')

params_p %>% 
  dplyr::mutate(valence = factor(valence, levels = c("Good", "Neutral", "Bad")),
                matchness = ifelse(matchness == 'Mismatch', 'Nonmatch', matchness),
                identity = factor(identity, levels = c('Self', 'Other'))) %>%
  ggplot2::ggplot(., aes(x = v, y = a, group = valence, color = valence)) +
  geom_point() + 
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  facet_grid(identity ~ matchness) +
  #facet_grid(~ matchness) +
  ylab(expression(paste("Boundary separation ",italic("a"), sep = ' '))) +
  xlab(expression(paste("Drift rate ",italic("v"), sep = ' '))) +
  theme_bw()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          text=element_text(family='Times'),
          legend.title=element_blank(),
          legend.text = element_text(size =16),
          plot.title = element_text(lineheight=.8, face="bold", size = 18, margin=margin(0,0,20,0)),
          axis.text = element_text (size = 16, color = 'black'),
          axis.title = element_text (size = 16),
          #axis.title.x = element_blank(),
          #axis.title.y = element_blank(),
          axis.line.x = element_line(color='black', size = 1),    # increase the size of font
          axis.line.y = element_line(color='black', size = 1),    # increase the size of font
          strip.text = element_text (size = 16, color = 'black'), # size of text in strips, face = "bold"
          panel.spacing = unit(3, "lines")
    ) 
```

We fitted our data with HDDM, using the response-coding [also see @Hu_2020_GoodSelf]. We estimated separate drift rate ($v$), non-decision time ($T_{0}$), and boundary separation ($a$) for each condition. We found that, similar to experiment 3a, the shapes tagged with good person has higher drift rate and higher boundary separation than shapes tagged with both neutral and bad person, but only for the self-referential condition. Also, the shapes tagged with neutral person has a higher drift rate than shapes tagged with bad person, but not for the boundary separation, and this effect also exist only for the  self-referential condition. 

Interestingly, we found that  in both self-referential and other-referential conditions, the shapes associated bad valence have higher drift rate and higher boundary separation. which might suggest that the shape associated with bad stimuli might be prioritized in the non-match trials (see figure \@ref(fig:plot-exp6b-HDDM))).