---
title: "Analyizing the Behavioral Data of Experimental 1"
author: "Chuan-Peng Hu"
date: "Sunday, Feb 18, 2018"
output: word_document
---

<style type="text/css">

body{ /* Normal  */
   font-family: Times     
   font-size: 12px;
}
td {  /* Table  */
   font-size: 8px;
}
h1 { /* Header 1 */
 font-size: 28px;
}
h2 { /* Header 2 */
 font-size: 22px;
}
h3 { /* Header 3 */
 font-size: 18px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 10px;
}
pre { /* Code block */
  font-size: 10px
}
</style>


This script is 

```{r Initializing, include=FALSE}
source('Initial.r')
```

# Experiment 1a 

```{r loadingDatadf1a,echo=FALSE,results='hide'}
# load the preprocessed data (long-format) 
df1a_d  <- read.csv("exp1a_dprime_long.csv",header = TRUE, sep = ",",stringsAsFactors=FALSE,na.strings=c("","NA"))
df1a_rt <- read.csv("exp1a_rt_acc_long.csv",header = TRUE, sep = ",",stringsAsFactors=FALSE,na.strings=c("","NA"))

# read the preprocessed data (wide-format)
df1a_w <- read.csv("exp1a_behav_wide.csv",header = TRUE, sep = ",",stringsAsFactors=FALSE,na.strings=c("","NA"))

```

## Participants
57 college students were recruited (38 female, age = 20.75 ± 2.54 years. 39 college students were from Tsinghua University community in 2014; 18 additional college students were recruited at Wenzhou University in 2017. The additional data were collected to get at least 50 participants as suggestion by Simmons, Nelson, and Simonsohn (2013)). All participants were right-handed except one, and all had normal or corrected-to-normal vision. Informed consent was obtained from all participants prior to the experiment according to procedures approved by a local ethics committee. 6 participant’s data was excluded from analysis because nearly random level of accuracy (4 participants from the Tsinghua community and 2 from the Wenzhou community), leaving 51 participants (34 female, age = 20.72 ± 2.44 years).

##Results
Correct responses shorter than 200 ms were excluded from the analysis, eliminated 0.04% of the trials overall. Table 1 shows the accuracy and Reaction times(RTs) of paired trials in Experiment 1. 

###Analaysis of d prime
```{r analyzing d prime df1a, echo=FALSE, results='hide',warning=FALSE, message=FALSE}
# RM-anova for d prime
df1a.d_anova1 <- ezANOVA(df1a_d,dv = dprime, wid = Subject, within=.(Morality), type=3)
print(df1a.d_anova1)

# t-test
# moral vs immoral
df1a.d.mrl_imm <- t.test(df1a_w$d_Moral,df1a_w$d_Immoral,paired = TRUE)
df1a_w$d_mrl_imm <- df1a_w$d_Moral - df1a_w$d_Immoral
df1a.d.mrl_imm.CI <- bootES(df1a_w$d_mrl_imm,R = 20000, effect.type = "cohens.d")

df1a.d.tvalue.mrl_imm <- round(as.numeric(df1a.d.mrl_imm[[1]]),3)
df1a.d.df1a.d.mrl_imm <- as.numeric(df1a.d.mrl_imm[[2]])
df1a.d.pvalue.mrl_imm.adj <- p.adjust(as.numeric(df1a.d.mrl_imm[[3]],"bonferroni",3))
df1a.d.cohens.mrl_imm <- round(df1a.d.mrl_imm.CI[[1]],4) 
df1a.d.CI.L.mrl_imm <- round(df1a.d.mrl_imm.CI[[12]][1],4)
df1a.d.CI.H.mrl_imm <- round(df1a.d.mrl_imm.CI[[12]][2],4)

# moral vs Average
df1a.d.mrl_ave <- t.test(df1a_w$d_Moral,df1a_w$d_Neutral,paired = TRUE)
df1a_w$mrl_ave <- df1a_w$d_Moral - df1a_w$d_Neutral
df1a.d.mrl_ave.CI <- bootES(df1a_w$mrl_ave,R = 20000, effect.type = "cohens.d")

df1a.d.tvalue.mrl_ave  <- round(as.numeric(df1a.d.mrl_ave[[1]]),3)
df1a.d.df1a.mrl_ave  <- as.numeric(df1a.d.mrl_ave[[2]])
df1a.d.pvalue.mrl_ave.adj <- p.adjust(as.numeric(df1a.d.mrl_ave[[3]],"bonferroni",3))
df1a.d.cohens.mrl_ave <- round(df1a.d.mrl_ave.CI[[1]],4) 
df1a.d.CI.L.mrl_ave <- round(df1a.d.mrl_ave.CI[[12]][1],4)
df1a.d.CI.H.mrl_ave <- round(df1a.d.mrl_ave.CI[[12]][2],4)

# Immoral vs. Average
df1a.d.imm_ave <- t.test(df1a_w$d_Immoral,df1a_w$d_Neutral,paired = TRUE)
df1a_w$imm_ave <- df1a_w$d_Immoral - df1a_w$d_Neutral
df1a.d.imm_ave.CI <- bootES(df1a_w$imm_ave,R = 20000, effect.type = "cohens.d")

df1a.d.tvalue.imm_ave <- round(as.numeric(df1a.d.imm_ave[[1]]),3)
df1a.d.df1a.imm_ave <- as.numeric(df1a.d.imm_ave[[2]])
df1a.d.pvalue.imm_ave.adj <- p.adjust(as.numeric(df1a.d.imm_ave[[3]],"bonferroni",3))
df1a.d.cohens.imm_ave <- round(df1a.d.imm_ave.CI[[1]],4) 
df1a.d.CI.L.imm_ave <- round(df1a.d.imm_ave.CI[[12]][1],4)
df1a.d.CI.H.imm_ave <- round(df1a.d.imm_ave.CI[[12]][2],4)


## plot and save the results of d'
df1a.V.SDT.sum <- summarySE(df1a_d,measurevar = 'dprime',groupvars = c('Morality'))
df1a.d.mean.ml <- round(df1a.V.SDT.sum$dprime[df1a.V.SDT.sum$Morality == 'Moral'],2)
df1a.d.sd.ml   <- round(df1a.V.SDT.sum$sd    [df1a.V.SDT.sum$Morality == 'Moral'],2)
df1a.d.mean.im <- round(df1a.V.SDT.sum$dprime[df1a.V.SDT.sum$Morality == 'Immoral'],2)
df1a.d.sd.im   <- round(df1a.V.SDT.sum$sd    [df1a.V.SDT.sum$Morality == 'Immoral'],2)
df1a.d.mean.av <- round(df1a.V.SDT.sum$dprime[df1a.V.SDT.sum$Morality == 'Neutral'],2)
df1a.d.sd.av   <- round(df1a.V.SDT.sum$sd    [df1a.V.SDT.sum$Morality == 'Neutral'],2)

df1a.V.SDT.sum$Morality <- factor(df1a.V.SDT.sum$Morality,levels = c('Moral','Neutral','Immoral'))

df1a.p_dprime <-ggplot(data = df1a.V.SDT.sum,aes(y = dprime, x = Morality, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +         # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = 0.2,
                      lwd = 1,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        #scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme  +
        theme(axis.text = element_text (size = 20, color = 'black')) + 
        theme(axis.title = element_text (size = 20)) + 
        theme(plot.title = element_text(size = 20)) +
        theme(legend.text = element_text(size =20)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20",'grey50', "grey80"),labels=c("Moral ",'Neutral  ',"Immoral"))+
        theme(axis.line.x = element_line(color="black", size = 1),
              axis.line.y = element_line(color="black", size = 1))

# ggsave('e1_dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

The effect of `r df1a.d_anova1[[1]][1,1]`: *F*(`r df1a.d_anova1[[1]][1,2]`, `r df1a.d_anova1[[1]][1,3]`) = `r round(df1a.d_anova1[[1]][1,4],3)`, *p* = `r round(df1a.d_anova1[[1]][1,5],4)`, $\eta_g^2$ = `r round(df1a.d_anova1[[1]][1,7],4)`

Then we conducted sample effect analysis for (see figure 1).

Moral (*d'* = `r df1a.d.mean.ml` $\pm$  `r df1a.d.sd.ml`) vs immoral  (*d'* = `r df1a.d.mean.im` $\pm$  `r df1a.d.sd.im`) association: *t*(`r df1a.d.df1a.d.mrl_imm`) = `r df1a.d.tvalue.mrl_imm`, *p* = 
`r df1a.d.pvalue.mrl_imm.adj`, *Cohen's* $d_z$ = `r df1a.d.cohens.mrl_imm`, 95% CI [`r df1a.d.CI.L.mrl_imm` `r df1a.d.CI.H.mrl_imm`]

Moral (*d'* = `r df1a.d.mean.ml` $\pm$  `r df1a.d.sd.ml`) vs. Average (*d'* = `r df1a.d.mean.av` $\pm$  `r df1a.d.sd.av`) Association: *t*(`r df1a.d.df1a.mrl_ave`) = `r df1a.d.tvalue.mrl_ave`, *p* = 
`r df1a.d.pvalue.mrl_ave.adj`, *Cohen's* $d_z$ = `r df1a.d.cohens.mrl_ave`, 95% CI [`r df1a.d.CI.L.mrl_ave` `r df1a.d.CI.H.mrl_ave`]

Immoral (*d'* = `r df1a.d.mean.im` $\pm$  `r df1a.d.sd.im`) vs. Average (*d'* = `r df1a.d.mean.av` $\pm$  `r df1a.d.sd.av`) association: *t*(`r df1a.d.df1a.imm_ave`) = `r df1a.d.tvalue.imm_ave`, *p* = 
`r df1a.d.pvalue.imm_ave.adj`, *Cohen's* $d_z$ = `r df1a.d.cohens.imm_ave`, 95% CI [`r df1a.d.CI.L.imm_ave` `r df1a.d.CI.H.imm_ave`]


```{r plot the d prime df1a, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df1a.V.SDT.sum,aes(y = dprime, x = Morality, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +         # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = 0.2,
                      lwd = 1,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        #scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme  +
        theme(axis.text = element_text (size = 20, color = 'black')) + 
        theme(axis.title = element_text (size = 20)) + 
        theme(plot.title = element_text(size = 20)) +
        theme(legend.text = element_text(size =20)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20",'grey50', "grey80"),labels=c("Moral ",'Neutral  ',"Immoral"))+
        theme(axis.line.x = element_line(color="black", size = 1),
              axis.line.y = element_line(color="black", size = 1))
```

###Analaysis of reaction time
```{r analyzing RT df1a,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
## plot density of each subject's RT and save them individually
subNo <- unique(df1a.V$Subject)
## doing the analysis for RT ####
df1a.V.RT <- df1a.V[df1a.V$ACC ==1,]  # exclued rt data less than 200 ms, and inaccurate data
df1a.V.RT.subj <- summarySEwithin(df1a.V.RT,measurevar = 'RT', withinvar = c('Subject','matchness','morality'), idvar = 'Subject',na.rm = TRUE)

df1a.V.RT.grand <- summarySE(df1a.V.RT.subj,measurevar = 'RT', groupvar = c('matchness','morality'),na.rm = TRUE)
df1a.V.RT_match <- df1a.V.RT[df1a.V.RT$matchness == "Match",]
df1a.V.RT_mismatch <- df1a.V.RT[df1a.V.RT$matchness == "Mismatch",]

df1a.rt_anova.match <- ezANOVA(df1a.V.RT_match,dv = RT, wid = Subject, within=.(morality),within_full=.(morality), type=3)
df1a.rt_anova.mismatch <- ezANOVA(df1a.V.RT_mismatch,dv = RT, wid = Subject, within=.(morality),within_full=.(morality), type=3)

## t-test for matched trials
df1a.V.RT.subj_w <- dcast(df1a.V.RT.subj, Subject ~ matchness + morality ,value.var = "RT") 

# moral vs. immoral
df1a.rt.t.m.mrl_imm <- t.test(df1a.V.RT.subj_w$Match_Moral,df1a.V.RT.subj_w$Match_Immoral,paired = TRUE)
df1a.V.RT.subj_w$m.mrl_imm <- df1a.V.RT.subj_w$Match_Moral - df1a.V.RT.subj_w$Match_Immoral
df1a.rt.t.m.mrl_imm.CI <- bootES(df1a.V.RT.subj_w$m.mrl_imm, R = 20000,effect.type = "cohens.d")

df1a.rt.tvalue.mrl_imm  <- round(as.numeric(df1a.rt.t.m.mrl_imm [[1]]),3)
df1a.rt.df1a.mrl_imm  <- as.numeric(df1a.rt.t.m.mrl_imm [[2]])
df1a.rt.pvalue.mrl_imm.adj <- p.adjust(as.numeric(df1a.rt.t.m.mrl_imm [[3]],"bonferroni",3))
df1a.rt.cohens.mrl_imm <- round(df1a.rt.t.m.mrl_imm.CI[[1]],4) 
df1a.rt.CI.L.mrl_imm <- round(df1a.rt.t.m.mrl_imm.CI[[12]][1],4)
df1a.rt.CI.H.mrl_imm <- round(df1a.rt.t.m.mrl_imm.CI[[12]][2],4)

# moral vs. average
df1a.rt.t.m.mrl_ave <- t.test(df1a.V.RT.subj_w$Match_Moral,df1a.V.RT.subj_w$Match_Average,paired = TRUE)
df1a.V.RT.subj_w$m.mrl_ave <- df1a.V.RT.subj_w$Match_Moral - df1a.V.RT.subj_w$Match_Average
df1a.rt.t.m.mrl_ave.CI <- bootES(df1a.V.RT.subj_w$m.mrl_ave, R = 20000,effect.type = "cohens.d")

df1a.rt.tvalue.mrl_ave <- round(as.numeric(df1a.rt.t.m.mrl_ave [[1]]),3)
df1a.rt.df1a.mrl_ave <- as.numeric(df1a.rt.t.m.mrl_ave[[2]])
df1a.rt.pvalue.mrl_ave.adj <- p.adjust(as.numeric(df1a.rt.t.m.mrl_ave[[3]],"bonferroni",3))
df1a.rt.cohens.mrl_ave <- round(df1a.rt.t.m.mrl_ave.CI[[1]],4) 
df1a.rt.CI.L.mrl_ave <- round(df1a.rt.t.m.mrl_ave.CI[[12]][1],4)
df1a.rt.CI.H.mrl_ave <- round(df1a.rt.t.m.mrl_ave.CI[[12]][2],4)

# immoral vs. average
df1a.rt.t.m.imm_ave <- t.test(df1a.V.RT.subj_w$Match_Immoral,df1a.V.RT.subj_w$Match_Average,paired = TRUE)
df1a.V.RT.subj_w$m.imm_ave <- df1a.V.RT.subj_w$Match_Immoral - df1a.V.RT.subj_w$Match_Average
df1a.rt.t.m.imm_ave.CI <- bootES(df1a.V.RT.subj_w$m.imm_ave, R = 20000,effect.type = "cohens.d")

df1a.rt.tvalue.imm_ave <- round(as.numeric(df1a.rt.t.m.imm_ave[[1]]),3)
df1a.rt.df1a.imm_ave  <- as.numeric(df1a.rt.t.m.imm_ave[[2]])
df1a.rt.pvalue.imm_ave.adj <- p.adjust(as.numeric(df1a.rt.t.m.imm_ave[[3]],"bonferroni",3))
df1a.rt.cohens.imm_ave <- round(df1a.rt.t.m.imm_ave.CI [[1]],4) 
df1a.rt.CI.L.imm_ave <- round(df1a.rt.t.m.imm_ave.CI[[12]][1],4)
df1a.rt.CI.H.imm_ave <- round(df1a.rt.t.m.imm_ave.CI[[12]][2],4)

df1a.V.RT.grand.match <- df1a.V.RT.grand[df1a.V.RT.grand$matchness == "Match",]
df1a.rt.mean.ml <- round(df1a.V.RT.grand.match$RT[df1a.V.RT.grand.match$morality == 'Moral'],0)
df1a.rt.sd.ml <- round(df1a.V.RT.grand.match$sd[df1a.V.RT.grand.match$morality == 'Moral'],0)
df1a.rt.mean.im <- round(df1a.V.RT.grand.match$RT[df1a.V.RT.grand.match$morality == 'Immoral'],0)
df1a.rt.sd.im <- round(df1a.V.RT.grand.match$sd[df1a.V.RT.grand.match$morality == 'Immoral'],0)
df1a.rt.mean.av <- round(df1a.V.RT.grand.match$RT[df1a.V.RT.grand.match$morality == 'Average'],0)
df1a.rt.sd.av <- round(df1a.V.RT.grand.match$sd[df1a.V.RT.grand.match$morality == 'Average'],0)

df1a.p_rt <- ggplot(data = df1a.V.RT.grand.match, aes(x=morality,y=RT,group=morality,shape = morality,fill = morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +         # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(y = 'Reaction times (ms)') +
        coord_cartesian(ylim=c(500,800))+
        scale_y_continuous(breaks = seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
        apatheme +
        theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
# ggsave('e1_RT_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot

tiff(filename = "Figure 1a. d prime and RTs of Experiment 1a.tiff", width = 8, height = 6, units = 'in', res = 300)
multiplot(df1a.p_dprime,df1a.p_rt,cols = 2)
dev.off()

```

We conducted two repeated measure ANOVA for RT of matched trials and mismatched trials separately
For the matched trials, 
The effect of `r df1a.rt_anova.match[[1]][1,1]`: *F*(`r df1a.rt_anova.match[[1]][1,2]`, `r df1a.rt_anova.match[[1]][1,3]`) = `r round(df1a.rt_anova.match[[1]][1,4],3)`, *p* = `r round(df1a.rt_anova.match[[1]][1,5],4)`, $\eta_g^2$ = `r round(df1a.rt_anova.match[[1]][1,7],4)`

For the nonmatched trials, 
The effect of `r df1a.rt_anova.mismatch[[1]][1,1]`: *F*(`r df1a.rt_anova.mismatch[[1]][1,2]`, `r df1a.rt_anova.mismatch[[1]][1,3]`) = `r round(df1a.rt_anova.mismatch[[1]][1,4],3)`, *p* = `r round(df1a.rt_anova.mismatch[[1]][1,5],4)`, $\eta_g^2$ = `r round(df1a.rt_anova.mismatch[[1]][1,7],4)`

Then we conducted sample effect analysis for the matched trials.

Moral (RT = `r df1a.rt.mean.ml` $\pm$ `r df1a.rt.sd.ml`) vs immoral (RT = `r df1a.rt.mean.im` $\pm$ `r df1a.rt.sd.im`) association : *t*(`r df1a.rt.df1a.mrl_imm`) = `r df1a.rt.tvalue.mrl_imm`, *p* = `r df1a.rt.pvalue.mrl_imm.adj`, *Cohen's* $d_z$ = `r df1a.rt.cohens.mrl_imm`, 95% CI [`r df1a.rt.CI.L.mrl_imm` `r df1a.rt.CI.H.mrl_imm`]

Moral (RT = `r df1a.rt.mean.ml` $\pm$ `r df1a.rt.sd.ml`) vs. average  (RT = `r df1a.rt.mean.av` $\pm$ `r df1a.rt.sd.av`) association: *t*(`r df1a.rt.df1a.mrl_ave`) = `r df1a.rt.tvalue.mrl_ave`, *p* = `r df1a.rt.pvalue.mrl_ave.adj`, *Cohen's* $d_z$ = `r df1a.rt.cohens.mrl_ave`, 95% CI [`r df1a.rt.CI.L.mrl_ave` `r df1a.rt.CI.H.mrl_ave`]

Immoral (RT = `r df1a.rt.mean.im` $\pm$ `r df1a.rt.sd.im`) vs. average (RT = `r df1a.rt.mean.av` $\pm$ `r df1a.rt.sd.av`) association: *t*(`r df1a.rt.df1a.imm_ave`) = `r df1a.rt.tvalue.imm_ave`, *p* = `r df1a.rt.pvalue.imm_ave.adj`, *Cohen's* $d_z$ = `r df1a.rt.cohens.imm_ave`, 95% CI [`r df1a.rt.CI.L.imm_ave` `r df1a.rt.CI.H.imm_ave`]


```{r plot the RT1 df1a, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# df1a.V.RT.grand.match <- df1a.V.RT.grand[df1a.V.RT.grand$matchness == "match",]
ggplot(data = df1a.V.RT.grand.match, aes(x=morality,y=RT,group=morality,shape = morality,fill = morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +         # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'Reaction times (ms)') +
        coord_cartesian(ylim=c(500,800))+
        scale_y_continuous(breaks = seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
        apatheme +
        theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```

The above is the reaction time for each condition
